% File: Liu_coverletter_embed.tex
% Project: 2022-05-30
% Created Date: 2021-05-04T18:33:01-04:00
% Author: Liu (Zuguang Liu)
% -----
% Last Modified: 2022-05-30T09:17:23-05:00
% Modified By: Liu (Zuguang Liu)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plain Cover Letter
% LaTeX Template
% Version 1.0 (28/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute
% http://www.rpi.edu/dept/arc/training/latex/resumes/
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt]{letter} % Default font size of the document, change to 10pt to fit more text

\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font
%\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font
\usepackage{hyperref}

% Margins
\topmargin=-1in % Moves the top of the document 1 inch above the default
\textheight=8.5in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa

\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right

\begin{document}

%----------------------------------------------------------------------------------------
%	ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

\begin{letter}
    {\vspace{-15pt}}

    %----------------------------------------------------------------------------------------
    %	YOUR NAME & ADDRESS SECTION
    %----------------------------------------------------------------------------------------

    \begin{center}
        \large \textbf{Liu} (Zuguang Liu) \\ % Your name
        %\vspace{20pt} \hrule height 1pt % If you would like a horizontal line separating the name from the address, uncomment the line to the left of this text
        2805 W Larchmont Ln A31, Peoria, IL 61615 \\
        (513)886-6058 \\
        \href{mailto:leo85811nardo@protonmail.com}{leo85811nardo@protonmail.com}
    \end{center}


    \signature{Liu (Zuguang Liu)} % Your name for the signature at the bottom

    %----------------------------------------------------------------------------------------
    %	LETTER CONTENT SECTION
    %----------------------------------------------------------------------------------------

    \opening{Dear Sir or Madam,}

    \par I am writing to express my interest in the full-time opportunity with the engineering department in your company.

    \par I studied Electrical Engineering in University of Cincinnati
    with a minor in Mathematics and Embedded systems and a great interest
    in robotics.
    While persuing in the same field at graduate school after receiving
    Bachelor's Degree, I was offered for a full-time embedded software engineer
    role at L\&T Techlonogies in Peoria, IL.
    Over the 8 months working at L\&T, though still interested in the embedded
    programming aspects, I find it hard to feel passionate on the subjects of
    the projects.
    Your job posting left me an impression that you are looking for engineers
    for robotics development.
    This aligns exactly with my original interest from college, which is why
    I'm applying to this position.

    \par My current employer, L\&T Technologies is an engineering consulting
    firm.
    My current work at L\&T involves maintaining and troubleshooting
    embedded firmware for Catepillar transmission Electronic Control Module,
    as well as developing automated testing framework for the software in a
    virtual simulated environment.
    Previously, I had Co-op at Ethicon Inc, a company that develops medical
    surgery devices.
    Over the internship I prototyped a PCB as part of a medical power generator,
    then developed the firmware and UI for the mechanical team.
    Over the time I was in college, I participated in many robotics-related
    projects, including Computer Vision development for UC Robotics, control
    system engineering for levitation pod in the Hyperloop Competition for my
    college team, as well as designing and implementing the control software for
    a semi-autonomous tunnel boring machine for the Boring Competition.

    For more info about my professional and project experiences, you can visit
    my \href{https://liu2z2.github.io/}{website}.

    \par I wish to have an opportunity to work for your company if this job is still available.
    I am currently an F1 student who is just starting my 2-year STEM extension,
    available from August 2022 and able to relocate anywhere nationwide given the time.
    Please let me know if there any questions or interest.

    \par Thank you for your consideration.

    \closing{Sincerely yours,}


    %\encl{Curriculum vitae, employment form} % List your enclosed documents here, comment this out to get rid of the "encl:"

    %----------------------------------------------------------------------------------------

\end{letter}

\end{document}