%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plain Cover Letter
% LaTeX Template
% Version 1.0 (28/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute 
% http://www.rpi.edu/dept/arc/training/latex/resumes/
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt]{letter} % Default font size of the document, change to 10pt to fit more text

\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font 
%\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font
\usepackage{hyperref}

% Margins
\topmargin=-1in % Moves the top of the document 1 inch above the default
\textheight=8.5in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa

\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right

\begin{document}

%----------------------------------------------------------------------------------------
%	ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

\begin{letter}
{\vspace{-15pt}} 

%----------------------------------------------------------------------------------------
%	YOUR NAME & ADDRESS SECTION
%----------------------------------------------------------------------------------------

\begin{center}
\large \textbf{Liu} (Zuguang Liu) \\ % Your name
%\vspace{20pt} \hrule height 1pt % If you would like a horizontal line separating the name from the address, uncomment the line to the left of this text
522 Riddle Rd Apt 18, Cincinnati, OH 45220 \\ (513)886-6058  \\ liu2z2@mail.uc.edu% Your address and phone number
\end{center} 


\signature{Liu (Zuguang Liu)} % Your name for the signature at the bottom

%----------------------------------------------------------------------------------------
%	LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------

\opening{Dear Sir or Madam,} 
 
I am writing to express my interest in the full-time/internship opportunity with the engineering department in your company. I knew about this job through the recruitment portal at my university and, after visiting your website, I believe my skills and background make me a good fit for the engineering position.  

I am currently studying Electrical Engineering in University of Cincinnati as an undergraduate, with a minor in Mathematics and Embedded systems, and will receive my Bachelor of Science degree in May 2021. While my college gave me comprehensive background in robotics, signal processing and programming, I decided to explore further in the Intelligent System track for graduate school. Through the ACCEND Program, I was able to classes in the area of data mining, deep learning and linear system theories. Your agency places prominence in similar areas. Having the privilege of working as an intern will offer me the skills and exposure that I need to advance my career while using what I have already learned to make an impact on your service and products. 

After graduation, while pursuing a master’s degree at the same college, I do hope to work for an agency and industry like yours to grow my experience in a professional setting. With the right opportunities, I believe that I can achieve my goal.

Previously, I had Co-oped at Ethicon Inc, a company that designs and engineers medical surgery devices. During that Co-op, I went through all phases in embedded system prototyping, including hardware designing, assembly, testing and software programming. My other working experience is at Jergens Inc, a manufacturing company where I implemented an automatic assembly system with controllers and mechatronics. When I am a full-time student, I like to work on small electronics/programming projects that interest me personally then archive them at my \href{https://liu2z2.github.io/tags#project-ref}{website} for documentation and showcase. 

I hope to have an opportunity to work for your company if this job is still available. Please let me know if there any questions or interest. 

Thank you for your consideration.

\closing{Sincerely yours,}


%\encl{Curriculum vitae, employment form} % List your enclosed documents here, comment this out to get rid of the "encl:"

%----------------------------------------------------------------------------------------

\end{letter}

\end{document}