% File: Liu_coverletter_ai.tex
% Project: 20210504Allout
% Created Date: 2021-05-04T18:33:01-04:00
% Author: Liu (Zuguang Liu)
% -----
% Last Modified: 2021-07-09T14:17:26-04:00
% Modified By: Liu (Zuguang Liu)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plain Cover Letter
% LaTeX Template
% Version 1.0 (28/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute
% http://www.rpi.edu/dept/arc/training/latex/resumes/
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt]{letter} % Default font size of the document, change to 10pt to fit more text

\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font
%\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font
\usepackage{hyperref}

% Margins
\topmargin=-1in % Moves the top of the document 1 inch above the default
\textheight=8.5in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa

\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right

\begin{document}

%----------------------------------------------------------------------------------------
%	ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

\begin{letter}
{\vspace{-15pt}}

%----------------------------------------------------------------------------------------
%	YOUR NAME & ADDRESS SECTION
%----------------------------------------------------------------------------------------

\begin{center}
\large \textbf{Liu} (Zuguang Liu) \\ % Your name
%\vspace{20pt} \hrule height 1pt % If you would like a horizontal line separating the name from the address, uncomment the line to the left of this text
522 Riddle Rd Apt 18, Cincinnati, OH 45220 \\ (513)886-6058  \\ liu2z2@mail.uc.edu% Your address and phone number
\end{center}


\signature{Liu (Zuguang Liu)} % Your name for the signature at the bottom

%----------------------------------------------------------------------------------------
%	LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------

\opening{Dear Sir or Madam,}

\par I am writing to express my interest in the full-time opportunity with the engineering department in your company.
After visiting your website and knowing this job, I believe my skills and background make me a good fit.

\par I studied Electrical Engineering in University of Cincinnati as an undergraduate, with a minor in Mathematics and Embedded systems, and received my Bachelor of Science degree in May this year.
While my college gave me comprehensive background in control systems, signal processing and programming, I decided to explore further in the intelligent system track for graduate school.
Through the ACCEND Program, I have expanded my study in the area of robotics, data mining and machine learning, during which I have largely improved my software development skills as well.
Your agency places prominence in similar areas.
Having the privilege of working at your company will offer me the skills and exposure that I need to advance my career while using what I have already learned to make an impact on your service and products.

\par In my most recent research in my school's MHCI lab, apart from applying data analysis methods to decompose and classify streamlined electroencephalogram (EEG) data, I helped with a robotic project integrates multiple AI-related principles including SLAM, NLP and BMI.
In my last Co-op at Ethicon, I designed and implemented a dynamic feedback control system for NFC sensors, which were used in the prototype machine for the team.
As a TA for a biology class that teaches students animal sensory with robotics, I implemented sensor fusion and computer vision algorithms as a backend method to the students' simulation.
When I am a full-time student, I like to work on small electronics/programming projects that interest me personally then archive them at my \href{https://liu2z2.github.io/tags#project-ref}{website} for documentation and showcase.

\par I wish to have an opportunity to work for your company if this job is still available.
I am currently an F1 student with a 3-year-long OPT, available now and able to relocate anywhere nationwide given the time.
Please let me know if there any questions or interest.

\par Thank you for your consideration.

\closing{Sincerely yours,}


%\encl{Curriculum vitae, employment form} % List your enclosed documents here, comment this out to get rid of the "encl:"

%----------------------------------------------------------------------------------------

\end{letter}

\end{document}