% File: Liu_coverletter_embed.tex
% Project: 20210504Allout
% Created Date: 2021-05-04T18:33:01-04:00
% Author: Liu (Zuguang Liu)
% -----
% Last Modified: 2021-06-15T19:24:23-04:00
% Modified By: Liu (Zuguang Liu)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plain Cover Letter
% LaTeX Template
% Version 1.0 (28/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute
% http://www.rpi.edu/dept/arc/training/latex/resumes/
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt]{letter} % Default font size of the document, change to 10pt to fit more text

\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font
%\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font
\usepackage{hyperref}

% Margins
\topmargin=-1in % Moves the top of the document 1 inch above the default
\textheight=8.5in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa

\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right

\begin{document}

%----------------------------------------------------------------------------------------
%	ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

\begin{letter}
    {\vspace{-15pt}}

    %----------------------------------------------------------------------------------------
    %	YOUR NAME & ADDRESS SECTION
    %----------------------------------------------------------------------------------------

    \begin{center}
        \large \textbf{Liu} (Zuguang Liu) \\ % Your name
        %\vspace{20pt} \hrule height 1pt % If you would like a horizontal line separating the name from the address, uncomment the line to the left of this text
        522 Riddle Rd Apt 18, Cincinnati, OH 45220 \\ (513)886-6058  \\ \href{mailto:liu2z2@mail.uc.edu}{liu2z2@mail.uc.edu}% Your address and phone number
    \end{center}


    \signature{Liu (Zuguang Liu)} % Your name for the signature at the bottom

    %----------------------------------------------------------------------------------------
    %	LETTER CONTENT SECTION
    %----------------------------------------------------------------------------------------

    \opening{Dear Sir or Madam,}

    \par I am writing to express my interest in the full-time opportunity with the engineering department in your company.
    After visiting your website and knowing about this job, I believe my skills and background make me a good fit for the engineering position.

    \par I am studied Electrical Engineering in University of Cincinnati as an undergraduate, with a minor in Mathematics and Embedded systems, and just gradated in May this year.
    While I have a comprehensive background in electronics, signal processing and programming, I decided to focus my senior undergraduate study on Embedded Systems field.
    Your agency places prominence in similar areas.
    Having the privilege of working in your company will offer me the skills and exposure that I need to advance my career while using what I have already learned to make an impact on your service and products.


    \par Previously, I had Co-oped at Ethicon Inc, a company that designs and engineers medical surgery devices. During that Co-op, I went through all phases in embedded system prototyping, including hardware designing, assembly, testing and firmware programming.
    My other working experience is at Jergens Inc, a manufacturing company where I implemented an automatic assembly system with controllers and mechatronics.
    For my senior Capstone project, together with three other students, we designed a modular garden monitoring system as a proof-of-concept IoT device, and provided implementation with hardware, firmware and user application software.
    When I was a full-time student, I like to work on small electronics/programming projects that interest me personally then archive them at my \href{https://liu2z2.github.io/}{website} for documentation and showcase.

    \par I wish to have an opportunity to work for your company if this job is still available.
    I am currently in the application phase of my OPT and expect to have it by July 2021.
    Please let me know if there any questions or interest.

    \par Thank you for your consideration.

    \closing{Sincerely yours,}


    %\encl{Curriculum vitae, employment form} % List your enclosed documents here, comment this out to get rid of the "encl:"

    %----------------------------------------------------------------------------------------

\end{letter}

\end{document}