\documentclass[a4paper]{article}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\lhead{\footnotesize Statement of Interest}
\rhead{\footnotesize Zuguang Liu}
\begin{document}
\par My name is Zuguang Liu and I am writing to express my interest in pursuing
graduate study in Electrical and Computer Engineering at Bradley University.
\par During my undergraduate years at the University of Cincinnati, I enrolled
in the Electrical and Computer Engineering program, with a minor in Mathematics
and Embedded systems, and received my Bachelor of Science degree in May 2021.
Over my undergraduate study, I worked hard in my classes as well as in Co-op
(internships) and on-campus research labs.
Over one Co-op, I worked as an R\&D engineer at Ethicon Inc, a company that
designs and engineers medical surgery devices, where I was involved in
the development of the electrical system of a new product prototype.
My other working experience is at Jergens Inc, a manufacturing company where I
implemented an automatic assembly system with controllers and mechatronics.
In the MHCI research lab at the University of Cincinnati, I applied data
analysis methods to decompose and classify streamlined electroencephalogram
(EEG) data.
For my senior Capstone project, together with three other students, we designed
a modular garden monitoring system as a proof-of-concept IoT device, and
provided implementation with hardware, firmware, and user application software.
\par After I received my Bachelor of Science degree, I was also halfway in
completing my Master's Degree thanks to an experimental curriculum the
university offered.
While conflicted between continuing my graduate study and joining professional
engineering workforce, I was offered a full-time position at Caterpillar Inc. as
a software tester and validation engineer and worked for more than a year in the
same team up to now.
However, after talking to various people including my supervisor at work,
coworkers and professors at Bradley University, I decided to pick up my
graduate study again at Bradley University Electrical and Computer Engineering
Department.
\par I believe my academic achievements and professional experience up to now
has given me a great foundation for my future graduate study, as they could help
me relate to the real-world problem and scenarios I have encountered.
Furthermore, I also believe that at Bradley University, I will be able to make
connections with people who I can learn from.
For example, Dr. Jing Wang's current research focuses on robotics and controls,
which aligns well with my interest in intelligent robotic systems, so by
studying under him, I would also be able to share ideas with him in this area.
\par Thinking into the future, after completing my graduate study at Bradley
University, I hope I would be able to understand the technical aspect of my
current work at Caterpillar more.
I also hope by obtaining a Master's Degree, I can prove that I am an engineer
capable enough to accept and resolve more challenges, which leads to more
professional opportunities open to me.
\par Considering my extensive experience in Electrical and Computer Engineering
academically and professionally, I believe I am a capable and passionate student
for the ECE graduate program at Bradley University.
I look forward to starting another meaningful academic study for more advanced
education at Bradley University.
\end{document}